My title

### 2020-10-12 analysis/paper/paper2.Rmd
Article edits

---
title: "Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete"
subtitle: "Early Iron Age Cemeteries at Knossos"
author:
  - Dominic Pollard, Institute of Archaeology, University College London
  - dominic.pollard.16@ucl.ac.uk
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/articletemplate.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/world-archaeology.csl" # Insert path for the bib-style

>>>>

---
title: "Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete"
subtitle: "Early Iron Age Cemeteries at Knossos"
author:
  - Dominic Pollard
  - Institute of Archaeology, University College London, 31-34 Gordon Square, Bloomsbury, London WC1H 0PY, United Kingdom
  - dominic.pollard.16@ucl.ac.uk
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/articletemplate.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-anthropological-archaeology.csl" # Insert path for the bib-style

### 2020-10-12 analysis/templates/template.Rmd
Beginning writing
Article edits

---
title: "My title"
author:
- author 1
- other author
date: '`r Sys.Date()`'
output: word_document
abstract: "My abstract \n"
---

@@

```
output:
  word_document:
    reference_docx: templates/template1.docx
```

>>>>

---
title: "My title"
author:
- author 1
- other author
date: '`r Sys.Date()`'
output: word_document
highlights: "My highlights \n"
abstract: "My abstract \n"
---

@@

```
output:
  word_document:
    reference_docx: templates/articletemplate.docx
```
